---
title: "My First Quarto Document"
author: "Aaron Kessler"
date: "11/7/2022"
format:
  html:
    self-contained: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse) 
library(lubridate)
library(janitor)

```

### What is Quarto?

Text shows up here. You can type whatever you want...  
  
You can also do things like **bold some text** or *italicize* it. 
All kinds of other formatting things to play with too. 

# Header 1

## Header 2

### Header 3

Links - use a url or hyperlink to a phrase:

http://example.com

Look at my site [here](http://example.com). 


## Actually using R code
This is kind of important, right? Where do we put the R code itself?  
In what are called **chunks**. Like this:

```{r}

head(txhousing)

```

How do I make one of those? Either go to Insert -> R... or just CTRL/CMD + SHIFT + I  
  
Let's try it...

```{r}


```

So everything you put in the R chunk gets run as R code. This is essentially the reverse of what happens
in a regular R file -- where everything is code, and you comment out (#) the stuff that's explanatory text.  
Here, the reverse is happening: everything is explanatory text unless otherwise specified, and the R code
goes in the chunks.  
  
#### "In-line" R snippets
  
There's also one more option, which is you can embed a little bit of R code *within* your text. Like this:  
  
There were `r nrow(iris)` flowers in the iris dataset.

## Knitting

What is "knitting"...? Let's talk about it.  

Also one unsual thing about line breaks to be aware of -- the double-space.  
  
Now let's get to some actual data. We'll return to our presidential trips to explore.  

## PRESIDENTIAL TRIPS 

First we'll load the trips dataset

```{r}

events <- readRDS("events_saved.rds")

head(events)

```

Now let's do a quick filter...
```{r}

events %>% 
  filter(city == "Seattle")

```


### Finally - publishing options through the "YAML" 

When it comes to how are file are published (i.e. rendered), we have a bunch of different options that can help us
with certain types of circumstances.  
  
Let's look at a couple of them:

```
format:
  html:
    toc: true
    toc-location: left

```

What do the these *do*..? Let's try one at a time above.  
  
Then one more trick -- remember our date at the top?  

```
date: "2/9/2020"

```
  
That's fine if we only have one date we want to ever put on there. But let's say we want it to be 
the date we published our file. We'd have to keep manually changing it each time.  
Or would we?  

You can actually put R code directly into the YAML header too, like this:

```
date: "`r format(Sys.time(), '%B %d, %Y')`"

```
What is this doing? Let's try running the code itself in the console. Then we'll add it above and re-knit.





