---
title: "Joining Exercises"
author: "Your Name Here"
date: "`r format(Sys.time(), '%B %d, %Y')`"
format:
  html:
    self-contained: true
    toc: true
    toc-location: left
---

# Load the datasets

```{r}

counties_demographics <- readRDS("counties_demographics.rds")
counties_elexresults <- readRDS("counties_elexresults.rds")
counties_rural_urban_suburban <- readRDS("counties_rural_urban_suburban.rds")

```

# Exercises

Join together the election results and urban/suburban/rural tables above, and then use the merged table to:

-   filter for just Virginia

-   group/summarize to calculate the mean pct of Trump 2020 vote by urban/rural categories

```{r}




```

Take the grouped dataset, and create a column chart using ggplot to display it

```{r}




```

Now using the joined dataset, come up with two groupings you find interesting or newsworthy in a particular state, and replicate the steps above them them instead.

(i.e. instead of for urban/rural, perhaps you want to look at pct of white college grads in Michigan, etc. If you're having trouble, you can stick with Virginia as your state.)

```{r}




```
